Theorems and Definitions

### 2016-04-13 number_theory/hw/hw10.tex
another one on number

\item For an ordered pair $(a,b)\in\NN\times\NN$ we define the \textit{Generalized Prime Counting Map}
by \[\overline{\Omega}(a,b)=\Omega(a)-\Omega(b).\] If $(a,b),(c,d)\in\NN\times\NN$ are such that
$ad=bc$, prove that $\overline{\Omega}(a,b)=\overline{\Omega}(c,d)$.

>>>>

\item For an ordered pair $(a,b)\in\NN\times\NN$ we define the \textit{Generalized Prime Counting Map}
by \[\overline{\Omega}(a,b)=\Omega(a)-\Omega(b).\] If $(a,b),(c,d)\in\NN\times\NN$ are such that
$ad=bc$, prove that $\overline{\Omega}(a,b)=\overline{\Omega}(c,d)$.
\begin{quote}
Suppose $ad=bc$. We can write out the prime factorizations of $a,b,c$, and $d$ as
\begin{align*}
a &= p_{1}^{\alpha_{1}}p_{2}^{\alpha_{2}}\dots p_{n}^{\alpha_{n}}\\
b &= p_{1}^{\beta_{1}}p_{2}^{\beta_{2}}\dots p_{n}^{\beta_{n}}\\
c &= p_{1}^{\gamma_{1}}p_{2}^{\gamma_{2}}\dots p_{n}^{\gamma_{n}}\\
d &= p_{1}^{\delta_{1}}p_{2}^{\delta_{2}}\dots p_{n}^{\delta_{n}}.
\end{align*}
Then
\begin{align*}
ad&=p_{1}^{\alpha_{1}+\delta_{1}}p_{2}^{\alpha_{2}+\delta_{2}}\dots p_{n}^{\alpha_{n}+\delta_{n}}\\
bc&=p_{1}^{\beta_{1}+\gamma_{1}}p_{2}^{\beta_{2}+\gamma_{2}}\dots p_{n}^{\beta_{n}+\gamma_{n}}.
\end{align*}
We can consider $\overline{\Omega}(ad,bc)=\Omega(ad)-\Omega(bc)=0$. We know
$\Omega(ad)-\Omega(bc)=0$ since $ad=bc$ implies they will have the same prime factorization up to
permutation, so the powers of the prime factors of $ad$ will be equivalent to the powers of the prime
factors of $bc$. We now have
\begin{align*}
\Omega(ad)-\Omega(bc)&=(\alpha_{1}+\delta_{1})+(\alpha_{2}+\delta_{2})+\dots+(\alpha_{n}+\delta_{n})
- (\beta_{1}+\gamma_{1})-(\beta_{2}+\gamma_{2})-\dots-(\beta_{n}+\gamma_{n})\\
&= (\alpha_{1}+\alpha_{2}+\dots+\alpha_{n})-(\beta_{1}+\beta_{2}+\dots+\beta_{n})+
(\delta_{1}+\delta_{2}+\dots+\delta_{n})-(\gamma_{1}+\gamma_{2}+\dots+\gamma_{n})\\
&=\Omega(a)-\Omega(b)-\Omega(c)+\Omega(d)\\
&= 0.
\end{align*}
Then $\Omega(a)-\Omega(b)=\Omega(c)-\Omega(d)$, which by definition is
$\overline{\Omega}(a,b)=\overline{\Omega}(c,d)$.
\end{quote}
